Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-25 paper/paper.tex
pass on threats to validity

>>>>

As it is the case for most empirical evaluations, there are both
external and construct threats to validity associated to the results
we presented. In terms of external validity, our results might not
generalize to other test inputs and engines. To mitigate this threat,
we carefully selected inputs from various sources and cleaned them
according to a well-defined criteria. Considering the \js\ engines, we
used engines associated with the most popular browsers in the
market. In terms of construct validity, there might be errors in the
implementation of our infrastructure. To mitigate this threat, we
extensively inspected the results of our evaluation manually and, when
we found the need for implementing a different component we kept the
old one for cross-checking. For example, we used
eshost-cli~\cite{eshost-cli} to validate our fork-join implementation
of the ``Checker'' component from Figure~\ref{fig:workflow} that, for
efficiency, is tighly integrated to our infrastructure.
